Treatment planning for HDR Brachytherapy

### 2015-03-29 Paper Seminar/isim_paper.tex
Merge I guess.
Added introductary paragraph. Additional libtex source, therefore lib.bib updated.

\title{Treatment planning for HDR Brachytherapy}
\date{March 30, 2015}
\author{S.~Elm \and
T.~Karthe \and
M.~E.~Schroeder \and
%D.~Golebiewski \and
L.~Mordhorst}

@@

>>>>

\title{Treatment planning for HDR Brachytherapy}
\date{March 31st, 2015}
\author{S.~Elm \and
T.~Karthe \and
M.~E.~Schroeder \and
D.~Golebiewski \and
L.~Mordhorst
}

@@

\section{Introduction}
High dose rate brachytherapy (abbreviated: hdr brachytherapy) as a conformal radiation therapy allows a much higher cancer tissue ratio, compared to other treatment approaches. During hdr brachytherapy, radioactive sources (i.e. seeds) are placed within the patient's body, in, close to and around the cancer tissue. Then, the seeds eradiate into the surrounding tissues, remaining a pre-calculated time frame (dwell time). Therefore, seed placement and dwell times are the most important factors when analyzing brachytherapy treatments \cite{brachytherapy}. \\
The focus of this article is set upon optimizing the dwell times for a fixed seed placement using computer aided algorithms, i.e. genetic algorithms and linear programming, as well as step-wise linear programming. The different algorithms will be described. Further on, they are analyzed and evaluated upon their adjustment possibilities (like parameters). Additionally, conclusions about the quality of the resulting treatment plans are drawn. Lastly, a possible approach to reduce runtim complexity and reuse of prior knowledge is presented.
